\frb: Very Large Array Burst Properties and Implications for Overall FRB Population

### 2016-11-16 repeater-vladata.tex
added rate text

\subsection{Temporal Statistics}
Burst detections were made very inhomogenously though the roughly 60 hours of observing toward FRB 121102. In the first $\sim8$\ hours of observing at L-band and the first $\sim25$\ hours observing at S-band no bursts were detected. Finally, in the last $\sim27$ hours of S-band observing, all nine bursts were detected. Data quality are relatively high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution not an observational artifact.

@@

Bursts seem to drop throughout last campaign. The nominal rate is 1e-4 per second, but a someone higher rate is inferred from modeling shown in Figure \ref{fig:rate}.

@@

Discussion of ``red spectrum'' and Connor \& Pen. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...

@@

\section*{Acknowledgements}
We thank ...
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.

>>>>

\subsection{Temporal Statistics}

Burst detections were made very inhomogenously though the roughly 63 hours of observing toward FRB 121102. Data quality are relatively high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution not an observational artifact.

In the first $\sim25$\ hours observing at S-band no bursts were detected, while nine bursts were detected in the last $\sim30$ hours of S-band observing. Assuming the burst detection probability follows a stationary Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.12$ hour$^{-1}$. The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$. The inconsistency shows that the detection probability is not stationary.

Moreover, there is weak evidence that the \frb burst rate changes during the last part of the campaign. We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time as $R=a + b*(\rm{MJD} - 57623)$. We then calculated the probability of measuring the observed event rate as $\Pi P_i(R)$. Figure \ref{fig:rate} shows the ($a$, $b$) parameter space with contours of 50, 90, and 95\% confidence contours.

Figure \ref{fig:ls} shows a Lomb-Scargle periodogram...
Lots of excess power corresponding to periods shorter than 1 hour.

@@

@@

Discussion of ``red spectrum'' and \citet{2016MNRAS.458L..89C}. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...

@@

\section*{Acknowledgements}
We thank ...
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.. This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
